Conflict-Free Vertex Coloring Of Planar Graphs

### 2017-02-21 paper/paper.tex
Key points and outline

\section*{KEY POINTS}
The goal of this research is to discover and explain properties and results of conflict-free coloring of planar graphs. The conflict-free coloring problem is a variation of the classical vertex coloring problem (VCP). The VCP aims to color a graph \(G = (V, E)\) such that no two adjacent vertices receive the same color. This is typically shown in the form of the \emph{k-colorability} problem: a graph is \emph{k-colorable} if it can be colored using $k$ or less colors. For example, the map of the 48 contiguous states can be colored with 4 colors and is thus \emph{4-colorable}. This is shown in the famous four-color theorem. It cannot be colored with 3 colors, and is thus \emph{not 3-colorable}.

@@

A conflict-free coloring is a variation of the VCP. Each vertex must be assigned a color such that for every vertex $v$, there is at least one color appearing exactly once in the neighborhood of $v$, i.e. vertices adjacenct to $v$.

@@

\section{Background}
\label{sec:background}
Give some of the needed background regarding graph theory, complexity theory (i.e. NP-complete, NP-hard, etc), and the classical vertex coloring problem.

\subsection{Graphs}
\label{sec:graphs}
Define what a graph, \(G = (V, E)\), is. Define terms that will be used throughout the paper dealing with graphs such as nodes, edges, neighborhoods, etc.

@@

\subsection{Complexity of the VCP}
\label{sec:complexitytheory}

\section{Conclusions}

\section{Acknowledgments}
Give thanks to my mom, etc.

\cite{bondy1976graph}

>>>>

\section*{KEY POINTS}
The goal of this research is to discover and explain properties and results of conflict-free (C-F) coloring of planar graphs. The conflict-free coloring problem is a variation of the classical vertex coloring problem (VCP). The VCP aims to color a graph \(G = (V, E)\) such that no two adjacent vertices receive the same color. This is typically shown in the form of the \emph{k-colorability} problem: a graph is \emph{k-colorable} if it can be colored using $k$ or less colors. For example, the map of the 48 contiguous states can be colored with 4 colors and is thus \emph{4-colorable}. This is shown in the famous four-color theorem. It cannot be colored with 3 colors, and is thus \emph{not 3-colorable}.

@@

A conflict-free coloring is a variation of the VCP. Each vertex must be assigned a color such that for every vertex $v$, there is at least one color appearing exactly once in the neighborhood of $v$, i.e. vertices adjacent to $v$. My primary source by Abel et al. \cite{abel2017three} focuses on results of conflict-free colorings of general graphs and then moves into the specific case of planar graphs.

There are many complexity results relating to conflict-free colorings. Conflict-free coloring is reduced from the \emph{k-colorability} to show that it is NP-hard. We know that \emph{k-colorability} is NP-hard through a reduction from 3-SAT. The reduction of \emph{3-SAT} to \emph{k-colorability} is given in \cite{sharma2012new}. This source then goes on to give results for C-F coloring of planar graphs. For example, \cite{abel2017three} give results on the NP-completeness of deciding whether planar graphs can be C-F colored with 1 or 2 colors. Conflict-free coloring of planar graphs can always be done with 3 colors, but minimizing the colors used is NP-hard, like the original VCP.

For general graphs, there are complexity results given by \cite{gargano2015complexity}. They show that conflict-free coloring of closed neighborhoods (when a node does not belong to its neighborhood) is NP-complete. They give non-approximability results for the conflict-free coloring of open neighborhoods.

@@

\section{Background}
\label{sec:background}
Give some of the needed background regarding graph theory, complexity theory (i.e. NP-complete, NP-hard, etc), and the classical vertex coloring problem. Background information will generally come from \cite{bondy1976graph}.

\subsection{Graphs}
\label{sec:graphs}
Define what a graph, \(G = (V, E)\), is. Define terms that will be used throughout the paper dealing with graphs such as nodes, edges, neighborhoods, what a planar graph is, etc.

@@

\subsection{Complexity Theory}
\label{sec:complexitytheory}
Define common complexity theory terms such as P, NP, NP-complete, and NP-hard. Talk about the complexity of the classical VCP and define other knowledge needed to talk about complexity.

\section{C-F Coloring of General Graphs}
Discuss conflict-free coloring of general graphs, i.e. graphs that can be non-planar.
\section{C-F Coloring of Planar Graphs}
Discuss conflict-free coloring of planar graphs.

\section{Complexity of Coloring C-F Graphs}
Discuss the complexity of coloring C-F graphs.

\subsection{General Graphs}
\subsubsection{Open Neighborhoods}
This is when the neighborhood of a node does not include the node itself.

\subsubsection{Closed Neighborhoods}
This is when the neighborhood of the node includes the node itself. Talk about result that conflict-free coloring of closed neighborhoods is NP-complete from \cite{gargano2015complexity}.

\subsection{Planar Graphs}
Look at the complexity results given in \cite{abel2017three} at coloring planar graphs.

\section{Conclusions}
Brief summary of the findings and results explained above.

\section{Acknowledgments}
Give thanks to my mom, Peter, Elena, etc.
